\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
PAPARRRR

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
\end{abstract}
\thispagestyle{empty} %remove page number from title page, but still keep it as pg #1
\newpage
\thispagestyle{empty}
\tableofcontents
\thispagestyle{empty}
\mbox{}
\newpage

@@

Because performance is dependent on instruction optimization, the most efficient programs are compiled specifically for a certain processor architecture. In order to reduce space, tweetNaCl cannot provide optimal run-time performance. \cite{TweetNaCl} While tweetNaCl is not fully optimized for the processor, the impact on a low-volume cryptographic communication like the CubeSat is minimal.

@@

\end{multicols}
\clearpage
%cite all the references from the bibtex you haven't explicitly cited
\nocite{*}
%break long urls with lots of hyphens
\def\UrlBreaks{\do\/\do-}

>>>>

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
As satellite communication becomes more accessible with the introduction of CubeSats, the need for authenticated and encrypted communication become necessary to protect against attackers. We have developed a lightweight, open-source cryptographic library suitable for satellites, specfically CubeSats, based on the NaCl and TweetNaCl libraries. The library, LiteCrypto, includes authentication, encryption, and authenticated encryption for IPv4 packets under symmetric keys.

\end{abstract}
\thispagestyle{empty} %remove page number from title page, but still keep it as pg #1
\newpage
\thispagestyle{empty}
\tableofcontents
\thispagestyle{empty}
\mbox{}
\newpage

@@

Because performance is dependent on instruction optimization, the most efficient programs are compiled specifically for a certain processor architecture. In order to reduce space, tweetNaCl cannot provide optimal run-time performance. \cite{TweetNaClPaper} While tweetNaCl is not fully optimized for the processor, the impact on a low-volume cryptographic communication like the CubeSat is minimal.

@@

The LiteCrypto library is available at https://github.com/WardenGnaw/LiteCrypto. It is available for anyone to use and modify. After further testing with CubeSat, LiteCrypto will hopefully be integrated for use.

From this this project, we have learned that we should not roll our own crypto,  keep libraries small and simple, and the last important lesson is always to deal with it.
\end{multicols}
\clearpage
%cite all the references from the bibtex you haven't explicitly cited
\nocite{*}
%break long urls with lots of hyphens
\def\UrlBreaks{\do\/\do-}
